\Large \bf Relationship of Weather and Maize Yields in Kenya

### 2018-11-15 writing/draft1/draftMonika6.tex
adding
working hardly
working

>>>>

{\hspace{-1.5cm}
\begin{threeparttable}
\singlespacing
\caption{\textit{\textbf{Mixed  effects model:} Log of maize yield and weather, ARMA(1,1) errors}}
%KEN11a
\label{KenARe11} 
\begin{footnotesize}

\begin{tabular}{llrllll}

\hline \vspace{-0.2cm} \\
\vspace{-0.2cm} \\
  \multicolumn{1}{l}{\vspace{0.1cm}\textbf{ }}  &\multicolumn{2}{c}{\textit{All counties}} &\multicolumn{2}{c}{\textit{ASAL}} &\multicolumn{2}{c}{\textit{non-ASAL}}\\
    \multicolumn{1}{l}{\vspace{0.1cm}\textbf{Fixed effects:}}&$exp(\beta)$&F-value%> anova(KEN11a, type='marginal')
    &$exp(\beta)$&F-value&$exp(\beta)$&F-value\\
 \hline 
\hline
\\
\vspace{-0.2cm}Intercept&$1.296$ $(1.060)^{***}$&$19.916$&$1.276$&$5.230$&$1.410^{}$&\\
  \\
\vspace{-0.2cm}Prec. total&$1.081$ $(1.034)^{*}$&$5.402$&$1.006^{**}$&$0.022$&$1.278^{**}$&\\
  \\
  \vspace{-0.2cm}Prec. total sq.&$0.973$ $(1.013)^{*}$&$4.289$&$1.004$&$0.051$&$0.880^{\bullet}$&\\
    \\
      \vspace{-0.2cm}Prec. c. of var.&$0.924$ $(1.044)^{\bullet}$&$3.277$&$0.969$ &$0.246$&$0.909^{}$\\
  \\

         \vspace{-0.2cm}Dry spell -length&$0.935$ $(1.031)^{*}$&$4.810$&$0.833$ ${}$&$6.969$&$ 0.988^{}$&\\
  \\
        \vspace{-0.2cm}Dry spells 	$\geq$ 4 d.&$0.939$ $(1.029)^{*}$&$4.826$&$0.855^{**}$&$8.065$&$0.989^{}$&\\
  \\
          \vspace{-0.2cm}Temp. - average&$0.819$ $(1.059)^{***}$&$12.127$&$0.808^{*}$&$5.376$&$0.878$ $^{}$&\\
  \\

          \vspace{-0.2cm}Temp. std. dev.&$1.043$ $(1.024)^{\bullet}$&$3.125$&$1.039$&$0.558$&$1.059$ ${*}$&\\
  \\

  \hline
\vspace{-0.2cm} \\
  \multicolumn{1}{l}{\textbf{Random effects:}}  & \\
\vspace{-0.2cm}
\\
\hline
\\
  \vspace{-0.2cm}Intercept\\
 \\ 
 \hline
\vspace{-0.2cm} \\
\textit{Number of observations:}  &$1300$&$698$& \\
\vspace{-0.2cm}
\\

  \hline
  \vspace{-0.2cm} \\
